PWD.KAZ

### 2019-07-16 results/PWD.KAZ.BivData.Rmd
small updates to setupdata and the analysis script

@@

>>>>

```{r}
#histograms to display the average number of Objects per cell
PWD.curateautoBivData_cells <- ddply(PWD_curate_BivData, c("fileName"), summarise,
                    number = length(Obj.ID)

PWD.autoBivData_cells_raw <- ggplot(data=PWD_BivData_cells, aes(x=boxs.IDd))+
  geom_histogram()+
  ggtitle("PWD raw bivadata")

PWD.autoBivData_cells <- ggplot(data=PWD.curateautoBivData_cells, aes(x=number))+
  geom_histogram()+   ggtitle("PWD curated")

PWD.autoBivData_cells_manu <- ggplot(data=PWD.auto.man_BivData_cells, aes(x=number))+
  geom_histogram()+
  ggtitle("PWD")

@@

```{r histograms}

KAZ.autoBivData_cells_raw <- ggplot(data=KAZ_BivData_cells, aes(x=boxs.IDd))+
  geom_histogram()+
  ggtitle("KAZ raw bivadata")
